Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-05-30 paper.tex
rephrased dummy's guide
Add files via upload

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work,
including Fermi-II acceleration with models of turbulent spectra
\citep{brunetti07,brunetti11}, injection scale of turbulence
\citep{miniati15}, the energy density of turbulence
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
for CR acceleration in shocks \citep[][in particular $K_{\rmn{ep}}$
  and the acceleration efficiency]{pinzke13}, and for cosmological
simulations with CR physics \citep[][i.e., shock history,
  temperature profile, density profile, magnetic field
  profile]{pinzke10}. All these parameters are uncertain, and could
potentially change our predictions. We refer the reader to
section~\ref{sect:param_comp} for a first exploration of parameter
space, however we leave the detailed exploration of parameter space and
the interaction between free parameters to future work.

@@

\subsection{Basic equations}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations. Because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles.

@@

\subsection{Dummy's guide} 
\label{sec:dummy}

All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{miniati15}:
\begin{equation}
D_{pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
\label{eqn:diffusion}
\end{equation}
\SPO{define $I_{\theta}(c_{s}/c)$ or explain its meaning in words and point to the definition provided in the next subsection.}
where
\begin{equation}
\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s} 
\end{equation}
is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}): 
\begin{equation}
\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
\label{eqn:Wk}
\end{equation}
which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes). Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering. Thus: 
\begin{equation}
D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
\end{equation}

@@

Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate. In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfv{\'e}n time $\tau_{\rm A}=l/\varv_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/\varv_{\rm l}$. 
Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$. If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta \varv \sim \varv_{\rm l})$ and cascade to smaller scales is $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim \varv_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time: 
\begin{equation}
\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
\end{equation}
where we have implicitly assumed isotropy. This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm A})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{A})^{1/4}$. Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum: 
\begin{equation}
E(k) \sim (\epsilon \varv_{\rm A})^{1/2} k^{-3/2}.
\end{equation}

@@

It can be shown that the particle pitch-angle averaged
momentum-diffusion coefficient of isotropic particles that couple to
fast magnetosonic modes via TTD resonance is \citep[][
  Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $\Vph$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $\varv_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

@@

\SPO{the derivation of the following is not transparent, could you expand?}
During reacceleration, the CRps increase their normalization
approximately by the factor
\begin{equation}
  \label{eq:Creacc}
  \delta C_\rmn{reacc.} \sim 
  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
\end{equation}
if injection and cooling are neglected. The reaccelerated CRs depend
exponentially on $\tau_D\sim 1/D_{pp}$ as long as $\tau_D \lesssim
\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
reacceleration of the merger which we assume to be 650~Myrs long.

@@

In this setion, we solve the Fokker-Planck equation for CR transport
on Lagrangian particle trajectories through cosmic history.  We
concentrate on three scenarios. (i) In model {\em M-primaries}, we
assume that CR electrons, which have been accelerated by cosmic
formation shocks and successively cooled by inverse Compton and
synchrotron losses, form a fossil seed population for
reacceleration. (ii) In model {\em M-streaming}, we account for the
outward streaming of central CRps, which produces a flat CR
distribution in the ICM and equivalently a flat secondary seed
population of CRe for reacceleration. (iii) In model {\em
  M-turbulence} we adopt a spatially flatter turbulent profile than
what was adopted before but assume that seed CRps and secondary CRes
follow the steep profile that is suggested by structure formation
simulations.

@@

Figure~\ref{fig:sync_profile} demonstrates that the modeled radio
profiles without turbulent reacceleration are too steep.  In the
bottom right panel of Fig.~\ref{fig:sync_profile} (labeled with
Brunetti et al. 2012), we show that our simulated profiles of
reaccelerated CRs, which only take advective CR transport into
account, i.e. they neglect CR streaming or a flatter turbulent
profile, produce radio profiles that are too steep. Indeed, even using
the assumptions of previous work -- where complete freedom in the seed
population was allowed -- it is not possible to reproduce observations
in both frequencies in any model.\footnote{Note that in previous work
  on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
  adopted which approximately corresponds to $\alpha_\rmn{tu}= 1$
  \citep{brunetti12} and together with the different distributions for
  seed CRes constitute the main differences compared to our work.}
Decreasing the acceleration efficiency with radius does not change
this conclusion much because of the weak radial dependence of
$D_\rmn{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
\sqrt{T(R)}$. This signals that the problem is generic and requires
either additional modifications to the plasma physics of acceleration
or a better understanding of potential observational systematics. In
addition there are differences in the simulated density and
temperature profiles in comparison to the observed profile in Coma
that impact the CR abundance as well as cooling and reacceleration.

In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
timescales in our three models scale with radius. As expected, the
\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
with $\tau_D\approx0.4\,\rmn{Gyr}$, where the small dip at large
radius driven by the decrease in thermal energy density. The
\Mflatturb model has the the flattest turbulent profile parameterized
by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_D$
profile. Note that a fixed reacceleration timescale is required to
explain the observations at each radius and for each model (see also
Table~\ref{tab:timescales}). This allows us to interchange the value
of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
i.e. a longer reacceleration duration have to be compensated by
lowering the level of turbulence or increasing the physical injection
scale of turbulence to keep $\tau_D$ constant.

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
  \caption{Turbulent reacceleration timescales for our simulated
    cluster g72a. We show in linear-log the reacceleration timescale
    ($\tau_D$) as a function of radius $R$ for our three models:
    \Mprimary (green dotted line), \Mstream (blue dashed line), and
    \Mflatturb (red solid line). Note that the timescales are derived
    during the last 100~Myrs in time in our simulations.}
  \label{fig:tauD}
\end{figure}

@@

As we have seen before, the most uncertain aspects of radio halo
emission models are the profile of compressible turbulence (which
determines the amount of Fermi II acceleration) and the distribution
of pre-existing CRs. Hence we vary parameters describing the amount of
energy contained in turbulence, $X_{\rm tu}$ (defined by $E_{\rm
  therm} = X_{\rm tu} E_{\rm therm}$), the spatial profile of
turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_0
\propto \epsilon_{\rm therm}^{\alpha_{\rm tu}}$, where $I_0^{} \propto
\varv_0^{3} k_0^{}$ is the injection rate of turbulence), as well as
the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
  spat}$ (see below).  We hold fixed thermal plasma properties
(temperature and density profiles), $B$-field profiles, total CR energy
content, and the turbulent outer scale (corresponding to a wavenumber
$k_{0}$). The CR energy content is suggested by our simulations
(observations only give an upper bound;
\citealt{2012ApJ...757..123A}). We focus on the uncertain CR
distribution rather than the overall normalization, since the impact
of the latter (an overall linear scaling) is clear.

@@

Larger levels of turbulence also {\it increase} spectral curvature, which might seem puzzling. It can be understood as follows. The pre-acceleration electron distribution function can be understood as a result of competition between hadronic injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling, which results in a quasi-steady state for the non-thermal (secondary) electrons. At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$. In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}). In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$. 
When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling. However, as the acceleration efficiency $A$ increases, radio emission starts to probe the 'bump' around $p_{*}$ (given by $\tau_{\rm D} \sim \tau_{\rm cool}(p_{*})$) where electrons accumulate and the distribution function is curved. This results in a curved emission spectrum. The synchrotron spectrum steepens at the frequency \citep{2001MNRAS.320..365B}: 
\begin{equation}
\nu_{\rm s} \propto \frac{B \tau_{\rm D}^{-2}}{(B^{2}+B^{2}_{\rm CMB})^{2}}
\end{equation}
where $B_{\rm CMB} \equiv (8 \pi U_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.

@@

While the requirement of a threshold level of turbulence may explain why radio brightness is bimodal, it also raises a fine-tuning problem: why is the $L_{\rm radio}$ vs. $L_{\rm X}$ relation in active radio halos so tight? Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}$--$L_{\rm X}$ relation. This can be only be understood if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter. We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.

>>>>

\AP{In section~\ref{sec:results} we pursue these three possibilities
  further and employ cosmological simulations of CRs in clusters. In
  tandem with new insights from our recent work on DSA generated
  fossil electrons \citep{pinzke13}, we generate the first
  quantitative calculation of primary and secondary seed electrons and
  compare to observations in the Coma cluster. For the most part, we
  adopt parameters that are used in previous work, including Fermi-II
  acceleration with models of turbulent spectra
  \citep{brunetti07,brunetti11}, injection scale of turbulence
  \citep{miniati15}, the energy density of turbulence
  \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
  for CR acceleration in shocks \citep[][in particular $K_{\rmn{ep}}$
    and the acceleration efficiency]{pinzke13}, and for cosmological
  simulations with CR physics \citep[][i.e., shock history,
    temperature profile, density profile, magnetic field
    profile]{pinzke10}. All these parameters are uncertain, and could
  potentially change our predictions. In section~\ref{sect:param_comp}
  we adopt a simplified spherical framework for our reacceleration
  model of secondary electrons. We perform a small parameter study and
  explore how radio emission depends on the parameters describing the
  spatial profile of CR protons and turbulence. In
  section~\ref{sect:param_comp} we discuss our results and present our
  conclusions.} \sout{We refer the reader to
  section~\ref{sect:param_comp} for a first exploration of parameter
  space, however} We leave the detailed exploration of parameter space
and the interaction between free parameters to future work.

@@

\subsection{Basic equations}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations. Because
they arise from a two body process, they are too centrally
concentrated. They also produce gamma-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles.

@@

\subsection{Physical picture of reacceleration}
\label{sec:dummy}

All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{miniati15}:
\begin{equation}
D_{pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
\label{eqn:diffusion}
\end{equation}
\SPO{define $I_{\theta}(c_{s}/c)$ or explain its meaning in words and point to the definition provided in the next subsection.}
where
\begin{equation}
\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s} 
\label{eqn:k_W} 
\end{equation}
is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}): 
\begin{equation}
\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
\label{eqn:Wk}
\end{equation}
which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes). Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering. Thus: 
\begin{equation}
D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
\end{equation}

@@

Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate. In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfv{\'e}n time $\tau_{\rm A}=l/\varv_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/\varv_{\rm l}$. 
Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$. If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta \varv \sim \varv_{\rm l})$ and cascade to smaller scales is $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim \varv_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time: 
\begin{equation}
\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
\label{eqn:cascade} 
\end{equation}
where we have implicitly assumed isotropy. This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm A})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{A})^{1/4}$. Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum: 
\begin{equation}
E(k) \sim (\epsilon \varv_{\rm A})^{1/2} k^{-3/2}.
\end{equation}

@@

It can be shown that the particle pitch-angle averaged
momentum-diffusion coefficient of isotropic particles that couple to
fast magnetosonic modes via TTD resonance is \citep[][
  Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $\Vph$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $\varv_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{\rm D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

@@

%\SPO{the derivation of the following is not transparent, could you
%  expand?}  \sout{During reacceleration, the CRps increase their
%  normalization approximately by the factor} \AP{In the region where
%  reacceleration dominates over cooling and injection, the CRps
%%  increase their normalization exponentially. This can easily be
 % understood by considering a simple toy model where a fossil CRp
%  population described by $f=C p^{-\alpha}$ is reaccelerated such that
%  $\tau_D < \tau_\rmn{cooling},\tau_\rmn{injection}$, i.e. injection
%  and cooling can be neglected. The Fokker-Planck equation in
%  Eqn.~\ref{eq:FP_p} then simplifies to}
%\begin{equation}
%  \dot{f} = {{\partial }\over{\partial p}}
%  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
%\end{equation}
%with the analytic solution given by
%\begin{equation}
%  \label{eq:Creacc}
%%  \delta C_\rmn{reacc.} \sim 
%  \exp{\left[\frac{(2+\alpha)(\alpha-1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,.
%\end{equation}
%The reaccelerated CRs depend exponentially on $\tau_D\sim 1/D_{pp}$ as
%long as $\tau_D \lesssim \tau_\rmn{cl}$, where $\tau_\rmn{cl}$
%represent the duration of reacceleration of the merger which we assume
%to be 650~Myrs long.

@@

In this section, we solve the Fokker-Planck equation for CR transport
on Lagrangian particle trajectories through cosmic history.  We
concentrate on three scenarios. (i) In model {\em M-primaries}, we
assume that CR electrons, which have been accelerated by cosmic
formation shocks and successively cooled by inverse Compton and
synchrotron losses, form a fossil seed population for
reacceleration. (ii) In model {\em M-streaming}, we account for the
outward streaming of central CRps, which produces a flat CR
distribution in the ICM and equivalently a flat secondary seed
population of CRe for reacceleration. (iii) In model {\em
  M-turbulence} we adopt a spatially flatter turbulent profile than
what was adopted before but assume that seed CRps and secondary CRes
follow the steep profile that is suggested by structure formation
simulations.

@@

Figure~\ref{fig:sync_profile} demonstrates that the modeled radio
profiles without turbulent reacceleration are too steep.  In the
bottom right panel of Fig.~\ref{fig:sync_profile} (labeled with
Brunetti et al. 2012), we show that our simulated profiles of
reaccelerated CRs, which only take advective CR transport into
account, i.e. they neglect CR streaming or a flatter turbulent
profile, produce radio profiles that are too steep. Indeed, even using
the assumptions of previous work -- where complete freedom in the seed
population was allowed -- it is not possible to reproduce observations
in both frequencies in any model.\footnote{Note that in previous work
  on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
  adopted which approximately corresponds to $\alpha_\rmn{tu}= 1$
  \citep{brunetti12} and together with the different distributions for
  seed CRes constitute the main differences compared to our work.}
Decreasing the acceleration efficiency with radius does not change
this conclusion much because of the weak radial dependence of
$D_{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
\sqrt{T(R)}$. This signals that the problem is generic and requires
either additional modifications to the plasma physics of acceleration
or a better understanding of potential observational systematics. In
addition there are differences in the simulated density and
temperature profiles in comparison to the observed profile in Coma
that impact the CR abundance as well as cooling and reacceleration.

In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
timescales in our three models scale with radius. As expected, the
\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
with $\tau_{\rm D}\approx0.4\,\rmn{Gyr}$, where the small dip at large
radius driven by the decrease in thermal energy density. The
\Mflatturb model has the the flattest turbulent profile parameterized
by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_{\rm D}$
profile. Note that a fixed reacceleration timescale is required to
explain the observations at each radius and for each model (see also
Table~\ref{tab:timescales}). This allows us to interchange the value
of uncertain parameters $\tau_\rmn{cl} \sim X_\rmn{tu}^2 \sim k_0$,
i.e. a longer reacceleration duration have to be compensated by
lowering the level of turbulence or increasing the physical injection
scale of turbulence to keep $\tau_{\rm D}$ constant.

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{tau_reacc.eps}
  \caption{Turbulent reacceleration timescales for our simulated
    cluster g72a. We show in linear-log the reacceleration timescale
    ($\tau_{\rm D}$) as a function of radius $R$ for our three models:
    \Mprimary (green dotted line), \Mstream (blue dashed line), and
    \Mflatturb (red solid line). Note that the timescales are derived
    during the last 100~Myrs in time in our simulations.}
  \label{fig:tauD}
\end{figure}

@@

As we have seen before, the most uncertain aspects of radio halo
emission models are the profile of compressible turbulence (which
determines the amount of Fermi II acceleration) and the distribution
of pre-existing CRs. Hence we vary parameters describing the amount of
energy contained in turbulence, $X_{\rm tu}$ (defined by $E_{\rm
  turb} = X_{\rm tu} E_{\rm th}$), the spatial profile of
turbulence as parametrized by $\alpha_{\rm tu}$ (defined by $I_0
\propto \epsilon_{\rm th}^{\alpha_{\rm tu}}$, where $I_0^{} \propto
\varv_0^{3} k_0^{}$ is the injection rate of turbulence), as well as
the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
  spat}$ (see below).  We hold fixed thermal plasma properties
(temperature and density profiles), $B$-field profiles, total CR energy
content, and the turbulent outer scale (corresponding to a wavenumber
$k_{0}$). The CR energy content is suggested by our simulations
(observations only give an upper bound;
\citealt{2012ApJ...757..123A}). We focus on the uncertain CR
distribution rather than the overall normalization, since the impact
of the latter (an overall linear scaling) is clear.

@@

Larger levels of turbulence also {\it increase} spectral curvature, which might seem puzzling. It can be understood as follows. The pre-acceleration electron distribution function results from the competition between hadronic injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling, which results in a quasi-steady state for the non-thermal (secondary) electrons. At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$. In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}). In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau_\rmn{D} =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$. 
When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling. However, as the acceleration efficiency $A$ increases, radio emission starts to probe the 'bump' around $p_{*}$ (given by $\tau_{\rm D} \sim \tau_{\rm cool}(p_{*})$) where electrons accumulate and the distribution function is curved. This results in a curved emission spectrum. The synchrotron spectrum steepens at the frequency \citep{2001MNRAS.320..365B}: 
\begin{equation}
\nu_{\rm s} \propto \frac{B \tau_{\rm D}^{-2}}{(B^{2}+B^{2}_{\rm CMB})^{2}}
\end{equation}
where $B_{\rm CMB} \equiv (8 \pi U_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.

@@

While the requirement of a threshold level of turbulence may explain why radio brightness is bimodal, it also raises a fine-tuning problem: why is the $L_{\rm radio}$ vs. $L_{\rm X}$ relation in active radio halos so tight? Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}$--$L_{\rm X}$ relation. This can be only be understood if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter. We address this next. %We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.

\subsection{Self-Limiting Turbulent Reacceleration}

There are 3 important timescales in this problem: the acceleration time $\tau_{\rm D}$, the duration that turbulence is active and acceleration takes place, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}(p)$. Only $\tau_{\rm cool}(p)$ is momentum dependent (and is different for ions and electrons). Thus, the outcome of acceleration depends essentially on two dimensionless numbers, $\tau_{\rm cl}/\tau_{\rm D}$, and $\tau_{\rm cool}/\tau_{\rm D}$.
